{\bf Landslide: A New Race-Finding Tool for 15-410}

### 2018-09-27 landslide-lecture/2018f/lecture.tex
study and survey resulce

\begin{document}
\renewcommand{\inserttotalframenumber}{38}
\normalem
\begin{frame}
	\titlepage
\end{frame}

@@

\begin{frame}{Previous Semesters}
	%% S'15, F'15, S'16: 48 groups signed up to use Landslide; 38 found bugs
	%% S'15, F'15, S'16, F'16, S'17: 79 groups signed up to use Landslide; 59 found bugs
	S'15, F'15, S'16, F'16, S'17, F'17: 94 groups signed up to use Landslide; 71 found bugs
	\linegap

	%%44 {\em deterministic} bugs (e.g. swexn, initialization)
	%% F17 lecture - stats up to S17
	%% 91 {\em deterministic} bugs (e.g. swexn, initialization)
	% S18 lecture - stats up to F17
	109 {\em deterministic} bugs (e.g. swexn, initialization)
	\linegap

	%%85 distinct {\em non-deterministic} bugs (among 32 groups)
	%% F17 lecture - stats up to S17
	%% 113 distinct {\em non-deterministic} bugs (among 44 groups)
	% S18 lecture - stats up to F17
	122 distinct {\em non-deterministic} bugs (among 49 groups)
	\begin{itemize}
		\item 36 groups (73\%) fixed $\ge 1$ such bug
		%\item 33 groups (75\%) fixed $\ge 1$ such bug
		%%\item 24 groups (75\%) fixed $\ge 1$ such bug
			\begin{itemize}
				\item (as verified by running Landslide again -- not a guarantee!)
			\end{itemize}
		\item 26 groups (53\%) fixed {\em all} such bugs
		%\item 24 groups (55\%) fixed {\em all} such bugs
		%%\item 15 groups (47\%) fixed {\em all} such bugs
		\item Most ambitious group: 11 distinct races found + fixed!
	\end{itemize}
	\linegap
\end{frame}

@@

>>>>

\begin{document}
\renewcommand{\inserttotalframenumber}{39}
\normalem
\begin{frame}
	\titlepage
\end{frame}

@@

\begin{frame}{Previous Semesters}
	%% S'15, F'15, S'16: 48 groups signed up to use Landslide; 38 found bugs
	%% S'15, F'15, S'16, F'16, S'17: 79 groups signed up to use Landslide; 59 found bugs
	%% S'15, F'15, S'16, F'16, S'17, F'17: 94 groups signed up to use Landslide; 75 found bugs % not sure why 75 -> 75
	%%S'15, F'15, S'16, F'16, S'17, F'17, S'18: 103 groups signed up to use Landslide; 75 found bugs
	S'15--S'18: 103 groups signed up to use Landslide; 75 found bugs
	\linegap

	% all this now from table 5.2 in thesis
	115 {\em deterministic} bugs (e.g. swexn, initialization)
	\begin{itemize}
		\item 87 (76\%) of these were fixed before submitting P2
			\begin{itemize}
				\item (as verified by running Landslide again -- not a guarantee!)
			\end{itemize}
	\end{itemize}
	\linegap

	122 distinct {\em non-deterministic} bugs
	\begin{itemize}
		\item 80 (66\%) of these were fixed before submitting P2
			\begin{itemize}
				\item (verified by running Landslide again, same)
			\end{itemize}
	\end{itemize}
	\linegap

	75 groups in total found any bugs
	\begin{itemize}
		\item 58 (77\%) groups fixed at least 1 bug
		\item 35 (47\%) groups fixed all found bugs
		\item Most ambitious group: 11 bugs found \& fixed!
	\end{itemize}
\end{frame}

\begin{frame}{Survey Results}
	F'17, S'18: Asked students what they thought of it all
	\begin{itemize}
		\item (also ran similar study at Penn State U. \& U. of Chicago)
	\end{itemize}

	\begin{center}
	\includegraphics[width=0.8\textwidth]{survey6.pdf}
	\end{center}
\end{frame}

\begin{frame}{Survey Results}
	\addtocounter{framenumber}{-1}
	F'17, S'18: Asked students what they thought of it all
	\begin{itemize}
		\item (also ran similar study at Penn State U. \& U. of Chicago)
	\end{itemize}

	\begin{center}
	\includegraphics[width=0.8\textwidth]{survey9.pdf}
	\end{center}
\end{frame}

\begin{frame}{Survey Results}
	\addtocounter{framenumber}{-1}
	F'17, S'18: Asked students what they thought of it all
	\begin{itemize}
		\item (also ran similar study at Penn State U. \& U. of Chicago)
	\end{itemize}

	\begin{center}
	\includegraphics[width=0.8\textwidth]{survey10.pdf}
	\end{center}
\end{frame}

@@

\begin{frame}{More Survey Results}
	(To dispel any accusations that I might have omitted survey questions with less good results)
	\linegap

	\begin{center}
	\includegraphics[width=0.8\textwidth]{survey1.pdf}
	\end{center}
\end{frame}

\begin{frame}{More Survey Results}
	(To dispel any accusations that I might have omitted survey questions with less good results)
	\linegap

	\begin{center}
	\includegraphics[width=0.8\textwidth]{survey2.pdf}
	\end{center}
\end{frame}

\begin{frame}{More Survey Results}
	(To dispel any accusations that I might have omitted survey questions with less good results)
	\linegap

	\begin{center}
	\includegraphics[width=0.8\textwidth]{survey3.pdf}
	\end{center}
\end{frame}

\begin{frame}{More Survey Results}
	(To dispel any accusations that I might have omitted survey questions with less good results)
	\linegap

	\begin{center}
	\includegraphics[width=0.8\textwidth]{survey4.pdf}
	\end{center}
\end{frame}

\begin{frame}{More Survey Results}
	(To dispel any accusations that I might have omitted survey questions with less good results)
	\linegap

	\begin{center}
	\includegraphics[width=0.8\textwidth]{survey5.pdf}
	\end{center}
\end{frame}

\begin{frame}{More Survey Results}
	(To dispel any accusations that I might have omitted survey questions with less good results)
	\linegap

	\begin{center}
	\includegraphics[width=0.8\textwidth]{survey7.pdf}
	\end{center}
\end{frame}

\begin{frame}{More Survey Results}
	(To dispel any accusations that I might have omitted survey questions with less good results)
	\linegap

	\begin{center}
	\includegraphics[width=0.8\textwidth]{survey8.pdf}
	\end{center}
\end{frame}
